A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-09 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
CWP Referee Comment improvements from Graeme (#110)
* Address first CSBS review comment about deployment consequences

It's quite hard to squeeze in changes like this, but what I did was minimal and should
be enough to satisfy the review point

* Address comment on Security and working with groups wider than HEP

* Add citation for ATLAS SLOC

* Add ATLAS ARM events/J reference

* Add dark silicon reference

* Add some Big Data tools references

* Remove out of place item about people from simulation section

* Correct double "the"

* Use more standard language for "near-real" time (referee co

\begin{itemize}
\item
  Reviewing the physics models' assumptions, approximations, and
  limitations in order to achieve higher precision, and to extend the
  validity of models up to energies of the order of 100 TeV foreseen
  with the Future Circular Collider (FCC) project~\cite{FCC}.
\item
  Redesigning, developing, and commissioning detector simulation
  toolkits to be more efficient when executed on current vector CPUs and
  emerging new architectures, including GPUs, where use of SIMD
  vectorisation is vital; this includes porting and optimising the
  experiments' simulation applications to allow exploitation of large
  HPC facilities.
\item
  Exploring different Fast Simulation options, where the full detector
  simulation is replaced, in whole or in part, by computationally
  efficient techniques. An area of investigation is common frameworks
  for fast tuning and validation.
\item
  Developing, improving and optimising geometry tools that can be shared
  am\-ong experiments to make the modeling of complex detectors
  computationally more efficient, modular, and transparent.
\item
  Developing techniques for background modeling, including contributions
  of multiple hard interactions overlapping the event of interest in
  collider experiments (pileup).
\item
  Revisiting digitisation algorithms to improve performance and
  exploring opportunities for code sharing among experiments.
\end{itemize}

>>>>

\begin{itemize}
\item
  Review the implementations of physics models, including the
  assumptions, approximations, and
  limitations. In the best cases this can achieve higher precision and
  improve runtime performance through code modernisation\cite{Novak2018}.
  The extension of the validity of models up to energies of 100 TeV is foreseen
  for the Future Circular Collider (FCC) project~\cite{FCC} and provides
  a good opportunity for this modernisation.
\item
  Redesigning, developing, and commissioning detector simulation
  toolkits to be more efficient when executed on current vector CPUs and
  emerging new architectures, including GPUs, where use of SIMD
  vectorisation is vital; this includes porting and optimising the
  experiments' simulation applications to allow exploitation of large
  HPC facilities.
\item
  Exploring different Fast Simulation options, where the full detector
  simulation is replaced, in whole or in part, by computationally
  efficient techniques. An area of investigation is common frameworks
  for fast tuning and validation.
\item
  Developing, improving and optimising geometry tools that can be shared
  am\-ong experiments to make the modeling of complex detectors
  computationally more efficient, modular, and transparent.
\item
  Developing techniques for background modeling, including contributions
  of multiple hard interactions overlapping the event of interest in
  collider experiments (pileup).
\item
  Revisiting digitisation algorithms to improve performance and
  exploring opportunities for code sharing among experiments.
\end{itemize}
